Skill estimation using TrueSkill Through Time: the \proglang{Julia}, \proglang{Python} and \proglang{R} packages

### 2021-04-29 doc/article.tex
Documentation version v0.0.0

\en{The \texttt{log_evidence()} method of the \texttt{History} class returns by default the product of all these elements in logarithmic scale.}

@@

\en{The variable \texttt{online} of the method \texttt{log_evidence()}, when assigned a true value, returns in logarithmic scale the product of the predictions made with past information.}

>>>>

\en{The \texttt{log\_evidence()} method of the \texttt{History} class returns by default the product of all these elements in logarithmic scale.}

@@

\en{The variable \texttt{online} of the method \texttt{log\_evidence()}, when assigned a true value, returns in logarithmic scale the product of the predictions made with past information.}
